\documentclass[letterpaper,11pt]{article}

% --- Packages ---
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor} % Upgraded for better color support
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}

% --- Typography / Font ---
% Using Helvetica for a clean, highly readable, modern sans-serif look
\usepackage[default]{carlito}\renewcommand{\familydefault}{\sfdefault}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

% --- Colors ---
% Define a professional blue color for headings
\definecolor{PrimaryBlue}{RGB}{20, 90, 150}
\definecolor{DarkGray}{RGB}{50, 50, 50}

% --- Page styling ---
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- Sections formatting ---
% Applied PrimaryBlue to the heading text and the rule below it
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{PrimaryBlue}
}{}{0em}{}[\color{PrimaryBlue}\titlerule \vspace{-5pt}]

% --- Custom commands ---
\newcommand{\resumeItem}[1]{
  \item\small{\color{DarkGray}
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\color{black}#1} & \color{PrimaryBlue}#2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \color{PrimaryBlue}#2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape \color{PrimaryBlue} Harish Kumar K} \\ \vspace{4pt}
    \small \textbf{Full Stack \& AI Engineer | AI-native Applications | Platform Engineering} $|$ 5+ Years Experience \\ \vspace{6pt}
    \small \color{DarkGray}
    \faMapMarker* Vellore, India \quad
    \faPhone* +91 8778257327 \quad
    \faEnvelope \hspace{1} \href{mailto:harishkumar.vellore@gmail.com}{harishkumar.vellore@gmail.com} \\ \vspace{3pt}
    \faGlobe \hspace{4px} \href{https://harishkumar.info}{harishkumar.info} \quad
    \faRss \hspace{4px} \href{https://harishkumar.info/blog}{Blog} \quad
    \faLinkedin \hspace{4px} \href{https://linkedin.com/in/harishkumark025}{linkedin.com/in/harishkumark025} \quad
    \faGithub \hspace{4px} \href{https://github.com/thelonewolf123}{github.com/thelonewolf123}
\end{center}
\vspace{4pt}

%-----------SUMMARY-----------
\section{Summary}
\small{\color{DarkGray}Full Stack \& AI Engineer with 5+ years of experience building production-grade AI systems, real-time applications, and distributed infrastructure. Strong expertise in \textbf{\color{black}LLM-powered tooling, observability, and systems engineering} — building products that combine AI with solid engineering. \textbf{\color{black}67+ pages of technical documentation} and \textbf{\color{black}12 published articles} on AI systems, real-time infrastructure, and distributed architecture.

Built three production-grade systems: \textbf{\color{black}Mail Pilot} (AI-native email client), \textbf{\color{black}Aegis} (AI-powered production debugging), and \textbf{\color{black}Stardust} (container platform on AWS Spot). Scaled a real-time platform to \textbf{\color{black}7,000+ users} with paying customers. Delivered measurable impact: \textbf{\color{black}150\% booking growth, 15min $\rightarrow$ 5s latency reduction, 55\% cost optimization}. Invited speaker at Chennai Web Conf (2025).}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {PickYourTrail}{11/2024 - Present}
      {Software Developer (SDE II)}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Migrated React Native \textbf{\color{black}0.76 $\rightarrow$ 0.82}, improving \textbf{\color{black}performance and stability}.}
        \resumeItem{Revamped \textbf{\color{black}hotel search and booking flow}, resulting in a \textbf{\color{black}150\% increase in bookings}.}
        \resumeItem{Built \textbf{\color{black}cancellation \& reschedule policy module} (core business workflow).}
        \resumeItem{Automated \textbf{\color{black}GST invoice retrieval from Indigo flights} (\textbf{\color{black}100--400} daily bookings).}
      \resumeItemListEnd

      \vspace{2pt}

    \resumeSubheading
      {BahiKhata Inc}{11/2023 - 11/2024}
      {Fullstack Developer}{Noida, India}
      \resumeItemListStart
        \resumeItem{Enabled \textbf{\color{black}offline and multi-session sync} for MSME transaction recording across devices without internet.}
        \resumeItem{Developed \textbf{\color{black}SMS parsing} to automatically detect and record transactions from bank messages.}
      \resumeItemListEnd

      \vspace{2pt}

    \resumeSubheading
      {Klenty}{02/2023 - 11/2023}
      {Full Stack Developer - Infra}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{\color{black}Zipkin distributed tracing} for system-wide observability.}
        \resumeItem{Built \textbf{\color{black}real-time mail tracking system} $\rightarrow$ reduced latency from \textbf{\color{black}15 min $\rightarrow$ 5 sec}.}
        \resumeItem{Designed \textbf{\color{black}request ID attribution} for MongoDB queries enabling exact user-to-code-path tracing.}
        \resumeItem{Built \textbf{\color{black}slow query detection pipeline} to identify and resolve performance bottlenecks.}
      \resumeItemListEnd

      \vspace{2pt}

    \resumeSubheading
      {Codedamn}{08/2022 - 02/2023}
      {Full Stack Developer - L3}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built \textbf{\color{black}DSA playground} for executing coding problems.}
        \resumeItem{Implemented \textbf{\color{black}real-time collaborative coding mode} (multi-user editor).}
        \resumeItem{Built \textbf{\color{black}autocomplete and IntelliSense system} for browser IDE.}
        \resumeItem{Optimized container allocation leading to a \textbf{\color{black}55\% cost reduction}.}
      \resumeItemListEnd

      \vspace{2pt}

    \resumeSubheading
      {Facilio}{03/2021 - 07/2022}
      {Member of Technical Staff}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Built advanced \textbf{\color{black}pivot table system} with conditional formatting and script columns for cross-module analytics.}
        \resumeItem{Designed \textbf{\color{black}custom computation engine} enabling spreadsheet-like dynamic analysis.}
      \resumeItemListEnd

      \vspace{2pt}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\color{black}Mail Pilot $|$ \emph{\small AI-Native Email Client}}{\href{https://mail-pilot-psi.vercel.app}{\textbf{Live}} \quad \href{https://harishkumar.info/docs/mail-pilot/}{\textbf{Docs}}}
          \resumeItemListStart
            \resumeItem{Built \textbf{\color{black}AI-native email client} where users control everything through natural language.}
            \resumeItem{Designed \textbf{\color{black}14 typed, Zod-validated AI tools} with a human-in-the-loop approval state machine for every email action.}
            \resumeItem{Built \textbf{\color{black}file reasoning} (PDF, CSV, text) and \textbf{\color{black}resume-to-job matching} powered by AI.}
            \resumeItem{Full technical documentation: \textbf{\color{black}25+ docs across 9 categories} covering architecture, AI agent system, and security.}
          \resumeItemListEnd
      \vspace{2pt}

      \resumeProjectHeading
          {\color{black}Aegis $|$ \emph{\small AI-Powered Production Debugging}}{\href{https://harishkumar.info/docs/aegis/}{\textbf{Docs}}}
          \resumeItemListStart
            \resumeItem{Built \textbf{\color{black}AI debugging system} that queries production databases, logs, and infrastructure via natural language.}
            \resumeItem{Multi-source correlation across PostgreSQL, CloudWatch, and IP geolocation with \textbf{\color{black}real-time SSE streaming}.}
            \resumeItem{Implemented \textbf{\color{black}5-layer defense-in-depth sandboxing}: Docker → iptables → NSJail → seccomp → read-only DB.}
            \resumeItem{Built \textbf{\color{black}ComputeFlow}: agent writes JS on-the-fly for data processing instead of dumping rows into LLM context.}
          \resumeItemListEnd
      \vspace{2pt}

      \resumeProjectHeading
          {\color{black}Stardust.app $|$ \emph{\small Container Deployment Platform — 6 microservices · 27 doc pages}}{\href{https://github.com/thelonewolf123/stardust.app}{\textbf{GitHub}} \quad \href{https://harishkumar.info/docs/stardust/}{\textbf{Docs}}}
          \resumeItemListStart
            \resumeItem{Built \textbf{\color{black}container provisioning engine on AWS Spot} with on-demand fallback and container checkpointing for disaster recovery.}
            \resumeItem{\textbf{\color{black}Real-time logs via SSE}, WebSocket SSH, and auto Docker builds triggered by git push.}
            \resumeItem{IaC with Pulumi, \textbf{\color{black}6 microservices} with RabbitMQ async orchestration, and 27 architecture docs.}
          \resumeItemListEnd
      \vspace{2pt}

      \resumeProjectHeading
          {\color{black}WatchWithMe $|$ \emph{\small Real-time Watch Party Platform}}{\href{https://www.watchwithme.in}{\textbf{Live}}}
          \resumeItemListStart
            \resumeItem{Built custom \textbf{\color{black}P2P WebRTC library from scratch} (DHT routing, in-browser relays); migrated \textbf{\color{black}4,000+ users} to LiveKit SFU with zero-downtime.}
            \resumeItem{Scaled to \textbf{\color{black}7,000+ users} with paying customers. Increased signup completion \textbf{\color{black}3x} through anonymous-first onboarding.}
            \resumeItem{Integrated voice + video chat and solved cross-platform sync, latency, and drift challenges.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{\hspace{4px} Achievements}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{\color{black}Invited Speaker} \quad $|$ \quad \emph{\small Chennai Web Conf}}{Dec 2025}
        \resumeItemListStart
          \resumeItem{\textbf{\color{black}Talk:} \textit{“Artemis: Personal AI OS”} — an AI productivity system integrating task management, note-taking, reminders, Perplexity-powered research, and voice interaction.}
          \resumeItem{Presented to 100+ engineers on building AI-native applications and personal AI systems.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{\color{DarkGray}
     \textbf{\color{black}Languages}{: TypeScript, JavaScript, Python} \\
     \textbf{\color{black}Frontend}{: React, React Native, Next.js, Tailwindcss, Shadcn} \\
     \textbf{\color{black}Backend}{: Node.js, Python, GraphQL, Express, FastAPI} \\
     \textbf{\color{black}Databases}{: PostgreSQL, MongoDB, Redis, MySQL} \\
     \textbf{\color{black}Gen AI \& LLM}{: LangGraph, CopilotKit, OpenRouter, n8n, RAG Pipelines}\\
     \textbf{\color{black}Cloud \& DevOps}{: AWS, Serverless, Docker, Pulumi} \\
     \textbf{\color{black}Core Strengths}{: Distributed Systems, Real-time Systems (WebSockets, Collaboration), Observability \& Debugging, AI-powered Tools}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thanthai Periyar Government Institute of Technology}{Vellore, India}
      {B.E Electronics and Communication Engineering}{2017 -- 2021}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}